### 2019-10-29 thesis/txt/2-models.tex
loads of new images, updates to the plotting, integrated images in study results

\chapter{Information Retrieval Techniques for Build Logs}
\plan{whole chapter: some reordering and reviewing to do, write about 3 pages about ir technique model classes and ir tasks and other techniques}
\plan{write, 1/3 page, blocked by: rest of chapter}
\label{sec:models}
%\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
Many different information retrieval techniques ... this section describes the conceptional / theoretical results of our thesis ...
We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly.
Additionally, we present a complementary model for IE tasks, to describe use cases for BLIE techniques in a structured way.
From our analysis of build logs, we share our notion of retrievable information within a build log.

@@

\section{Characteristics of a Build Log}
The idea of CI is, to integrate new software changes fast and often to catch errors early~\cite{humble2010continuous}.
After making a change, the developer commits and pushes it to a shared source code repository.
Companies often use a specific CI server, e.g.\ Travis CI, linked to their source code repository.
A CI build might then be triggered by a push on specific branches or after a pull request was created.
When such a CI build is triggered, it typically runs through these stages:

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/build-log-information.pdf}
	\caption{Information retrievable from build logs}
	\label{fig:build-log-information}
\end{figure}
\section{Retrievable Information in Build Logs}
Continuous integration build logs contain a huge amount of information about the stages in the CI build they correspond to.
In this section, we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
Figure \ref{fig:build-log-information} shows the model.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/ir-technique.pdf}
	\caption{Model for an Information Retrieval Technique}
	\label{fig:model-ie-technique}
\end{figure}
\section{Characteristics of Information Retrieval Techniques}
\plan{describe model classes, 1 page text}
For this thesis, we want to evaluate different information retrieval techniques when applied to CI build logs.
We focus on techniques that do not require to parse the structure of a whole build log, but rather focus on extracting just one specified information.
We refer to such a technique as BuildLogInformationRetrievalTechnique (BLIRT).

@@

\section{Information Retrieval Tasks}
\plan{what do we need here?, come up with model if we keep this, 1 page text max.}
Previous sections gave various examples of situations where a developer or a researcher wants to retrieve information from a build log.
The goal of this work is to clarify which BLIRT is suited for their specific task.
In this section we structure we present different important characteristics of such an IR task.
You can see the model in Figure \ref{fig:model-ir-task}

@@

\section{PROSE Program Synthesis}
\plan{2 caro-reviews before finalized}

@@

\section{Text Similarity}
\plan{2 caro-reviews before finalized}

@@

\section{Simple Keyword Search}
\plan{2 caro-reviews before finalized}

@@

\section{Further Techniques}
\plan{decide: what to mention here, max 1 page text}

Amar et al. used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section \ref{sec:rw-bl-analysis}.
Figure \ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.

>>>>

\chapter{Information Retrieval Techniques for Build Logs}
\plan{whole chapter: some reordering and reviewing to do, write about 3 pages about ir technique model classes and ir tasks and other techniques}
\plan{write, 1/3 page, blocked by: rest of chapter}
\label{sec:ir-techniques}
%\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
Many different information retrieval techniques ... this section describes the conceptional / theoretical results of our thesis ...
We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly.
Additionally, we present a complementary model for IE tasks, to describe use cases for BLIE techniques in a structured way.
From our analysis of build logs, we share our notion of retrievable information within a build log.

@@

\section{Characteristics of a Build Log}
\label{sec:bl-characteristics}
The idea of CI is, to integrate new software changes fast and often to catch errors early~\cite{humble2010continuous}.
After making a change, the developer commits and pushes it to a shared source code repository.
Companies often use a specific CI server, e.g.\ Travis CI, linked to their source code repository.
A CI build might then be triggered by a push on specific branches or after a pull request was created.
When such a CI build is triggered, it typically runs through these stages:

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/build-log-information.pdf}
	\caption{Information retrievable from build logs}
	\label{fig:build-log-information}
\end{figure}
\section{Retrievable Information in Build Logs}
\label{sec:bli}
Continuous integration build logs contain a huge amount of information about the stages in the CI build they correspond to.
In this section, we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
Figure \ref{fig:build-log-information} shows the model.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/ir-technique.pdf}
	\caption{Model for an Information Retrieval Technique}
	\label{fig:model-ie-technique}
\end{figure}
\section{Characteristics of Information Retrieval Techniques}
\label{sec:blirt}
\plan{describe model classes, 1 page text}
For this thesis, we want to evaluate different information retrieval techniques when applied to CI build logs.
We focus on techniques that do not require to parse the structure of a whole build log, but rather focus on extracting just one specified information.
We refer to such a technique as BuildLogInformationRetrievalTechnique (BLIRT).

@@

\section{Information Retrieval Tasks}
\label{sec:blir-tasks}
\plan{what do we need here?, come up with model if we keep this, 1 page text max.}
Previous sections gave various examples of situations where a developer or a researcher wants to retrieve information from a build log.
The goal of this work is to clarify which BLIRT is suited for their specific task.
In this section we structure we present different important characteristics of such an IR task.
You can see the model in Figure \ref{fig:model-ir-task}

@@

\section{Regular Expression Program Synthesis by Example}
\label{sec:expl-pbe}
\plan{2 caro-reviews before finalized}

@@

\section{Text Similarity}
\label{sec:expl-ts}
\plan{2 caro-reviews before finalized}

@@

\section{Simple Keyword Search}
\label{sec:expl-skws}
\plan{2 caro-reviews before finalized}

@@

\section{Further Techniques}
\label{sec:expl-rlr}
\plan{decide: what to mention here, max 1 page text}

\paragraph{Log Diff}
Amar et al. used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section \ref{sec:rw-bl-analysis}.
Figure \ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
\paragraph{Random Line Retrieval}
In our evaluation we want to compare against a basic deadline of randomly extracted lines.
The random line retrieval technique (RLR) averages the number of lines in the outputs of the configuring examples and extracts this many lines randomly from the build log.

### 2019-10-29 thesis/txt/5-study.tex
loads of corrections in ch2, literature, dev mails geschrieben und ausgewertet
loads of new images, updates to the plotting, integrated images in study results

\begin{figure}[h]
	\centering
	\includegraphics[page=6, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Process of our technique comparison study}
	\label{fig:study}
\end{figure}

\section{Method}
We configure the technique for every example set with an increasing count of I/O examples and then run the retrieval on the next I/O example, the \emph{test I/O example}.
The output from the test I/O example is the oracle for our evaluation.
The examples are sorted and selected chronologically, i.e. the technique is configured with examples from the directly preceeding build logs to extract information from the test log.
The extraction quality of a BLIRT run is evaluated on only one build log, as it should be suitable for every coming example.
Especially the one directly succeeding the configuration.
If the information retrieval there is bad, we expect the user to directly change the configuration again or be dissapointed with his selection of technique.

When evaluating a BLIRT run we measure the following data points:
\begin{itemize}
	\item \textbf{Successful} A BLIRT run is successful when the retrieved output contains all the lines the oracle output.
	\item \textbf{Accuracy} \todo{currently: levenstein difference of input and output, maybe: change to false pos and neg lines}
	\item \textbf{Proximity} \todo{can we usefully calculate that????}
\end{itemize}

@@

\section{Results}
\todo{accuracy (or so) of retrievals with growing example number // overall averages \& detailed look on special cases //}
\begin{figure}[hp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/accuracy-success-all.pdf}
		\caption{caption}
		\label{fig:accuracy-success-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/line-diff-all.pdf}
		\caption{caption}
		\label{fig:line-diff-all}
	\end{minipage}
\end{figure}

\begin{figure}[hp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/ouput-failed-pbe.pdf}
		\caption{caption}
		\label{fig:ouput-failed-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
		\caption{caption}
		\label{fig:success-all}
	\end{minipage}
\end{figure}

\begin{figure}[hp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
		\caption{caption}
		\label{fig:success-examples-ir}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
		\caption{caption}
		\label{fig:success-examples-kw}
	\end{minipage}
\end{figure}

\begin{figure}[hp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
		\caption{caption}
		\label{fig:success-examples-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
		\caption{caption}
		\label{fig:success-examples-pbe}
	\end{minipage}
\end{figure}

>>>>

\begin{figure}[htbp]
	\centering
	\includegraphics[page=6, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Process of our technique comparison study}
	\label{fig:study}
\end{figure}

\section{Method}
\bp{We compare three different techniques: PBE, TS, SKWS (itemize and link to their explanation?) and as a baseline: random line rerieval (RLR): retrieves random lines from the build log, (describe in chapper about BLIRTs??), number of lines: average of output lines from past}
We configure the technique for every example set with an increasing count of I/O examples and then run the retrieval on the next I/O example, the \emph{test I/O example}.
The output from the test I/O example is the oracle for our evaluation.
The examples are sorted and selected chronologically, i.e. the technique is configured with examples from the directly preceeding build logs to extract information from the test log.
The extraction quality of a BLIRT run is evaluated on only one build log, as it should be suitable for every coming example.
Especially the one directly succeeding the configuration.
If the information retrieval there is bad, we expect the user to directly change the configuration again or be dissapointed with his selection of technique.

When evaluating a BLIRT run we measure the following data points:
\begin{itemize}
	\item \textbf{Successful} A BLIRT run is successful when the retrieved output contains all the lines the oracle output.
	\item \textbf{Accuracy} \todo{currently: levenstein difference of input and output, maybe: change to false pos and neg lines}
	\item \textbf{Proximity} \todo{No! let's do that with "}
\end{itemize}

@@

\section{Results}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
	\caption{Distribution of Category Combinations in the Example Sets used for Configuration in our Study}
	\label{fig:categories-dataset}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/categorycount-examplecount-dataset.pdf}
		\caption{Distribution of the Count of Categories within the Examples used for Configuartion in our Study}
		\label{fig:categorycount-examplecount-dataset}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{caption}
		\label{fig:xxx}
	\end{minipage}
\end{figure}
\subsection{Category Distribution in Data Set}
Categories distributed in over data set
- why are we looking at that?: interesting how categories are distributed for this real world example of build Failure reasons in travis ci categorization
- Figure \ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
- Figure \ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.

\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
		\caption{Successful Extractions per Number of Examples for PBE}
		\label{fig:success-examples-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
		\caption{Successful Extractions per Number of Examples for TS}
		\label{fig:success-examples-ir}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
		\caption{Successful Extractions per Number of Examples for SKWS}
		\label{fig:success-examples-kw}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-rn.pdf}
		\caption{Successful Extractions per Number of Examples for RLR}
		\label{fig:success-examples-rn}
	\end{minipage}
\end{figure}

\subsection{Regular Expression Program Synthesis by Example}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
		\caption{Successful Extractions per Number of Examples for PBE}
		\label{fig:success-examples-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-pbe.pdf}
		\caption{Precision of Extractions per Number of Examples for PBE}
		\label{fig:precision-pbe}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-pbe.pdf}
		\caption{Precision of PBE Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-pbe.pdf}
		\caption{Reasons for PBE Runs to Fail}
		\label{fig:failure-reason-pbe}
	\end{minipage}
\end{figure}

This section addresses the results produced by the PBE technique in our study.
We start by comparing success rate and precision for different example counts and showing the influence of example categories.
Next we go into detail in which cases pbe fails
\subsubsection{Success-Rate}
\subsubsection{Precision}
\subsubsection{Example Categories}
\subsubsection{Specific Failure Reasons}
\todo{FAILURE REASON AGAINST EXAMPLE CATEGORIES}
% \subsection{Successful Extractions}
% successful is interpreted by us as: all lines that were desired (within our oracle) were also extracted during the test

% Figure \ref{fig:success-all} shows how successful the four different tecnhiques were in our study.
% Figure \ref{fig:success-examples-pbe} shows that the success rate for PBE decreases with increasing example count for pbe. Section \ref{TODO ref to pbe section} explains in more detail whi this fails
% Figure \ref{fig:success-examples-ir} shows that the success rate for TS varies but stays roughly the same for different example counts
% Figure \ref{fig:success-examples-kw} shows that the success rate for KWS varies but stays roughly the same for different example counts
% Figure \ref{fig:success-examples-pbe} shows that

\subsection{Text Similarity}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
		\caption{Successful Extractions per Number of Examples for TS}
		\label{fig:success-examples-ir}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-ir.pdf}
		\caption{Precision of Extractions per Number of Examples for TS}
		\label{fig:precision-ir}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-ir.pdf}
		\caption{Precision of TS Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-ir}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsubsection{Success-Rate}
\subsubsection{Precision}
\subsubsection{Example Categories}

\subsection{Simple Keyword Search}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
		\caption{Successful Extractions per Number of Examples for SKWS}
		\label{fig:success-examples-kw}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-kw.pdf}
		\caption{Precision of Extractions per Number of Examples for SKWS}
		\label{fig:precision-kw}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-kw.pdf}
		\caption{Precision of SKWS Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-kw}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsubsection{Success-Rate}
\subsubsection{Precision}
\subsubsection{Example Categories}

\subsection{Random Line Retrieval}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-rn.pdf}
		\caption{Successful Extractions per Number of Examples for RLR}
		\label{fig:success-examples-rn}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-rn.pdf}
		\caption{Precision of Extractions per Number of Examples for RLR}
		\label{fig:precision-rn}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-rn.pdf}
		\caption{Precision of RLR Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-rn}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

For completion this section reports the results for the random line retrieval technique, explained in detail in Section \ref{sec:}

\subsubsection{Success-Rate}
\subsubsection{Precision}
\subsubsection{Example Categories}

\subsection{Comparing All Techniques}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
		\caption{Successful Extractions for all Techniques Compared}
		\label{fig:success-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
		\caption{Precision of Extractions for all Techniques Compared}
		\label{fig:precision-all}
	\end{minipage}
\end{figure}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
		\caption{\todo{todo}}
		\label{fig:precision-category-singularity-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/single-cateogry-precision-all.pdf}
		\caption{\todo{todo}}
		\label{fig:single-cateogry-precision-all}
	\end{minipage}
\end{figure}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-all.pdf}
		\caption{\todo{todo}}
		\label{fig:precision-categorycount-examplecount-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{\todo{todo}}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsubsection{Success-Rate}
\subsubsection{Precision}
\subsubsection{Example Categories}
